\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins - optimized for one page
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.65in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - consistent spacing
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands - consistent spacing throughout
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Daniel Furmanov} \\ \vspace{2pt}
    \small
    \faIcon{phone} (718)-614-0080 $|$ 
    \faIcon{envelope} \href{mailto:danielfurmanov@hotmail.com}{\underline{danielfurmanov@hotmail.com}} $|$ 
    \faIcon{linkedin} \href{https://www.linkedin.com/in/daniel-furmanov/}{\underline{LinkedIn}} $|$
    \faIcon{github} \href{https://github.com/Acamerus}{\underline{GitHub}} \\
    \faIcon{flag-usa} Brooklyn, NY $|$ 
    \faIcon{language} Fluent in English and Intermediate in Russian
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Baruch College}
      {Aug 2025 -- May 2027}
      {Bachelor's in Computer Science: Financial Mathematics}{New York, NY}
    \resumeSubheading
      {Borough of Manhattan Community College}{Aug 2022 -- Aug 2025}
      {Associate's in Computer Science}{New York, NY}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
   \resumeSubheading
      {Software Developer/Project Manager Intern}{May 2025 -- Jul 2025}
      {\underline{\href{https://www.grasshopperairmobility.com/}{Grasshopper Air Mobility}}}{Barcelona, Spain}
      \resumeItemListStart
        \resumeItem{Researched and documented technical stack options (frontend, backend, database, hosting) and developed initial architecture for drone logistics tracking and order management system used by warehouse workers. }
        \resumeItem{Implemented application containerization using Podman in virtualized environments to reduce infrastructure costs and improve deployment efficiency. }
        \resumeItem{Collaborated with stakeholders and a 5-member team through 2 daily stand-up meetings, translating technical speak from the team to understandable terminology for the stakeholders.}
        \resumeItem{Hosting of full-stack project on Render for cost efficiency with documentation on how to deploy, suspend, redeploy, and delete if needed. }
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Physics Research Assistant}{Mar 2024 -- May 2024}
      {Borough of Manhattan Community College}{New York, NY}
      \resumeItemListStart
        \resumeItem{Operated Z3 Tensile Machine using GripSoft ZPM software, optimizing data recording processes.}
        \resumeItem{Created a custom manual simplifying machine operation for current and future assistants.}
        \resumeItem{Recorded and documented experimental results to be exported to Excel, enhancing data accuracy and research efficiency.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Product Management Intern}{Jul 2023 -- Aug 2023}
      {\underline{\href{https://unadat.com/}{Unadat}}}{Remote, NY}
      \resumeItemListStart
        \resumeItem{Developed customer-centric project plans, conducting market research to improve product outcomes.}
        \resumeItem{Utilized Asana's Sprint Planning features to define and track Sprint Goals, successfully delivering 12 potentially shippable products over 1 month.}
        \resumeItem{Lead Sprint Planning and Sprint Reviews for 5 cross-functional sub-teams, utilizing Asana's timeline and board views to visualize sprint goals and track progress against the Definition of Done (DoD). }
        \resumeItem{\underline{\href{https://drive.google.com/file/d/1lSTmuJKIGvZIinKhiqLikzGGo5gCskIr/view?usp=sharing}{Click to see: Supervisor Assessment/Evaluation Report.}}}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Mentorship Continuation Project} $|$ \emph{js, css, html, react, Vercel}}{Dec 2024 -- Jan 2025}
          \resumeItemListStart
        \resumeItem{Encouraged and promoted the continuation of the AI Innovation Challenge project from members who were involved during the challenge and recruited outside members to join under the direct mentorship of {\underline{\href{https://www.bmcc.cuny.edu/faculty/mohammad-azhar/}{Dr.Azhar.}}}}
        \resumeItem{Gathering all BMCC CS requirement courses, and prerequisites for each course to be formatted in json structure.}
        \resumeItem{Developed and hosted website using Vercel {\underline{\href{https://bmcc-guide.vercel.app/}{BMCC Guide.}}}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{BMCC AI Innovation Challenge} $|$ \emph{Python, Git, Tailscale, Streamlit, Requests, REST}}{Nov 2024 -- Nov 2024}
          \resumeItemListStart
            \resumeItem{Developed an AI-driven chatbot integrating DegreeWorks simulated data to provide personalized academic advising, progress tracking, and course planning for Computer Science students.}
            \resumeItem{Implemented a web scraper using Selenium to automate the retrieval of student data and degree progress information.}
           \resumeItem{Used Replete as a local LLM and REST APIs to enhance chatbot capabilities, improving accessibility to academic and wellness resources.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Course Database: Bank Loan Customers} $|$ \emph{SQL, Access, Database Modeling, Excel}}{Jun 2024 -- Jul 2024}
          \resumeItemListStart
            \resumeItem{Architected a banking database system using ER modeling and UML notation, normalized to BCNF across 6 core tables.}
            \resumeItem{Implemented complex SQL queries for data manipulation, including multi-table JOINs and subqueries for comprehensive reports.}
            \resumeItem{Developed a normalized Microsoft Access application with parameterized queries and custom VBA functions.}
            \resumeItem{Created an intuitive UI using Access forms with embedded macros and event procedures for real-time financial analytics.}
             \resumeItem{Produced a normalized Access/SQL database from Excel import to automate customer accounts and transactions, enhancing data integrity, security, and ability to add new data. }
          \resumeItemListEnd
  \resumeSubHeadingListEnd
 
%-----------TECHNICAL SKILLS-----------
\section{Awards \& Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Awards}: {\underline{\href{https://drive.google.com/file/d/1jiuWnsTUp3PDommo-ShgpSnyoEbazDzw/view?usp=sharing}{Gilman Alumni}}}, BMCC International Internship Scholarship, {\underline{\href{https://sites.google.com/view/bmcchacksai/fall-2024-winners/ai-innovation-track}{AI Innovation Challenge: Third Place Winner}}}, BMCC: Dean's List \\
     \textbf{Technical Skills}: SQL, Python, C++, Golang, JavaScript, CSS, HTML, JetSQL, Streamlit, Requests, React, Node \\
     \textbf{Tools \& Methodologies}: Git/Github, Bitbucket, Visual Studio Code, Tailscale, REST, Vercel, Podman, VIM, SupaBase, Microsoft Access, Agile, Methodologies, Asana, Trello, Jira, Slack, Teams, Leadership, Microsoft 360 Services, AI  \\
    }}
\end{itemize}

\end{document}
